Solving an optimization problem employing restraint programming

### 2015-12-13 proj2/doc/article.tex
added a lil bit moar

Concerning the restriction that a teacher can teach at most 15 hours per week,

>>>>

Concerning the restriction that a teacher can teach at most 15 hours per week, a number of predicates are in place that process and convert the input into formats that make it easy to gather the variables that concern the number of hours a teacher teaches per week. It is then said that the sum of these variables cannot exceed 15 (the code concerning this can be viewed in the annex, and will not be replicated here for reasons of spatial economy).
